---
title: "Hanauer's Method"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fama and Macbeth Regression

```{r}
library(data.table)
library(tidyr)
library(zoo)
library(dplyr)
library(janitor)
```

```{r}
load("../Univariate_Sort_Set.RData")
Univariate_Sort_Set <- as.data.table(Univariate_Sort_Set)
```

```{r}
ALL_FACTORS = c("Beta_3", "Sigma_3", "SD", "B/M", "B/Mm", "E/Pm", "C/Pm", "OP/BE", "NOA", "ROE", "AG", "CEI", "MV", "Log_MV", "Mom_12_2", "Alpha_3", "RSI")
```

```{r}
stock_size <- Univariate_Sort_Set
setorder(stock_size, ym, -MV.USD)
stock_big <- stock_size[!is.na(MV.USD), .(big = ifelse(((cumsum(MV.USD)/sum(MV.USD))>=0.9), 0, 1), Id), by=ym]
stock_big <- stock_big[big==1, c("Id", "ym")]
Univariate_Sort_Set_big <- merge(stock_big, Univariate_Sort_Set)
stock_big_small <- stock_size[!is.na(MV.USD), .(big_small = ifelse(((cumsum(MV.USD)/sum(MV.USD))>=0.97), 0, 1), Id), by=ym]
stock_big_small <- stock_big_small[big_small==1, c("Id", "ym")]
Univariate_Sort_Set_big_small <- merge(stock_big_small, Univariate_Sort_Set)
```

```{r}
results_lm <- function(data, x, y="ExRET.USD") {
  fm <- as.formula(paste(y, "~", paste(paste0("`", x, "`"), collapse = "+")))
  lm(fm, data = data)$coefficient
}

fm_reg <- function(data, x, y="ExRET.USD", group=c("ym")) {
  cols <- c(group, y, x)
  result <- data %>%
    select(all_of(cols)) %>%
    drop_na() %>%
    filter_all(all_vars(!is.infinite(.))) %>%
    group_by(across(all_of(group))) %>%
    reframe(
      coef=rbind(results_lm(pick(everything()), x))
    ) %>%
    ungroup()
  result <- as.data.table(result)
}

fm <- function(data, factor, y="ExRET.USD", group=c("ym"), reg_coef=FALSE) {
  reg_result <- fm_reg(data, factor, y, group)
  reg_result_only_value <- reg_result %>% select(-all_of(group))
  test_result <- sapply(reg_result_only_value, t.test)
  test_result <- test_result[c("estimate", "p.value"), -1]
  colnames(test_result) <- factor
  if (reg_coef) {
    names_coef <- c(group, "intercept", paste0("coef.", factor))
    colnames(reg_result) <- names_coef
    result <- list("test" = test_result, "reg" = reg_result)
    return(result)
  } else {
    return(test_result)
  }
}
```

## Big and Small Stocks (Excl. Micro)

```{r}
panel_a <- fm(Univariate_Sort_Set_big_small, c("Beta_3", "B/M", "OP/BE", "AG", "MV"))
panel_a
```

```{r}
panel_b <- fm(Univariate_Sort_Set_big_small, c("Beta_3", "Sigma_3", "SD", "B/M", "OP/BE", "AG", "MV"))
panel_b
```

```{r}
panel_c <- fm(Univariate_Sort_Set_big_small, c("Beta_3", "Sigma_3", "SD", "B/M", "OP/BE", "AG", "MV", "Mom_12_2"))
panel_c
```

```{r}
panel_d1 <- fm(Univariate_Sort_Set_big_small, c("Beta_3", "Sigma_3", "SD", "B/M", "B/Mm", "OP/BE", "AG", "MV", "Mom_12_2"))
panel_d1
```

```{r}
panel_d2 <- fm(Univariate_Sort_Set_big_small, c("Beta_3", "Sigma_3", "SD", "B/Mm", "E/Pm", "C/Pm", "OP/BE", "AG", "MV", "Mom_12_2"))
panel_d2
```

```{r}
panel_e <- fm(Univariate_Sort_Set_big_small, c("Sigma_3", "SD", "B/Mm", "OP/BE", "NOA", "ROE", "AG", "MV", "Mom_12_2"))
panel_e
```

```{r}
panel_f <- fm(Univariate_Sort_Set_big_small, c("Sigma_3", "SD", "B/Mm", "OP/BE", "NOA", "ROE", "AG", "CEI", "MV", "Mom_12_2"))
panel_f
```

```{r}
panel_g <- fm(Univariate_Sort_Set_big_small, c("Sigma_3", "SD", "B/Mm", "OP/BE", "NOA", "ROE", "CEI", "MV", "Log_MV", "Mom_12_2"))
panel_g
```

```{r}
panel_h <- fm(Univariate_Sort_Set_big_small, c("Sigma_3", "SD", "B/Mm", "NOA", "ROE", "CEI", "Log_MV", "Mom_12_2", "Alpha_3", "RSI"))
panel_h
```

```{r}
panel_i <- fm(Univariate_Sort_Set_big_small, c("Sigma_3", "B/Mm", "NOA", "CEI", "Log_MV", "Alpha_3", "RSI"))
panel_i
```

```{r}
result_final <- fm(Univariate_Sort_Set_big_small, c("Sigma_3", "B/Mm", "CEI", "Log_MV", "Alpha_3", "RSI"), reg_coef = TRUE)
panel_j <- result_final$test
coef_cross_sectional <- result_final$reg
panel_j
```

## Big Stocks

```{r}
panel_k1 <- fm(Univariate_Sort_Set_big, c("Beta_3", "B/M", "OP/BE", "AG", "MV"))
panel_k1
```

```{r}
panel_k2 <- fm(Univariate_Sort_Set_big, c("Sigma_3", "B/Mm", "NOA", "CEI", "Log_MV", "Alpha_3", "RSI"))
panel_k2
```

## Selected Factors: Sigma_3, B/Mm, NOA, CEI, Log_MV, Alpha_3, RSI

```{r}
load("~/Desktop/Summer Semester/Advanced Seminar/GBR/SS23_Empirical-Asset-Pricing/Data_Lewellen.RData")
```

```{r}
# merge with firm characteristics
data_set <- Univariate_Sort_Set_big_small %>% 
  select(Id, ym, MV.USD, RET.USD, MRP.USD, ExRET.USD, Sigma_3, `B/Mm`, NOA, CEI, Log_MV, Alpha_3, RSI)

lewellen_data_set <- merge(x=data_set, y=data_lewellen, by.x = c("ym"), by.y = c("ym"), all= 1)


# Creating the lag variable of mean36 average slope
lewellen_data_set[, Lag_mean36_Intercept := shift(mean36.intercept, n= 1), by = Id]
lewellen_data_set[, Lag_mean36_Sigma3 := shift(mean36.gamma.sigma3, n= 1), by = Id]
lewellen_data_set[, Lag_mean36_BMm := shift(mean36.gamma.bmm, n= 1), by = Id]
lewellen_data_set[, Lag_mean36_CEI := shift(mean36.gamma.cei, n= 1), by = Id]
lewellen_data_set[, Lag_mean36_Log_MV := shift(mean36.gamma.logmv, n= 1), by = Id]
lewellen_data_set[, Lag_mean36_Alpha3 := shift(mean36.gamma.alpha3, n= 1), by = Id]
lewellen_data_set[, Lag_mean36_RSI := shift(mean36.gamma.rsi, n= 1), by = Id]

# Creating the lag variable of cumulated average slope
lewellen_data_set[, Lag_cum_Intercept := shift(cummean.intercept, n= 1), by = Id]
lewellen_data_set[, Lag_cum_Sigma3 := shift(cummean.gamma.sigma3, n= 1), by = Id]
lewellen_data_set[, Lag_cum_BMm := shift(cummean.gamma.bmm, n= 1), by = Id]
lewellen_data_set[, Lag_cum_CEI := shift(cummean.gamma.cei, n= 1), by = Id]
lewellen_data_set[, Lag_cum_Log_MV := shift(cummean.gamma.logmv, n= 1), by = Id]
lewellen_data_set[, Lag_cum_Alpha3 := shift(cummean.gamma.alpha3, n= 1), by = Id]
lewellen_data_set[, Lag_cum_RSI := shift(cummean.gamma.rsi, n= 1), by = Id]

lewellen_expected_return_mean36 <- lewellen_data_set %>% 
  group_by(ym, Id) %>% 
  mutate(Expected_Return_36 = Lag_mean36_Intercept * intercept + Lag_mean36_Sigma3 * Sigma_3 + Lag_mean36_BMm * `B/Mm` + Lag_mean36_CEI * CEI + Lag_mean36_Log_MV * Log_MV + Lag_mean36_Alpha3 * Alpha_3 + Lag_mean36_RSI * RSI) %>% 
    ungroup

lewellen_expected_return_cummean <- lewellen_data_set %>% 
  group_by(ym, Id) %>% 
  mutate(Expected_Return_cummean = Lag_cum_Intercept * intercept + Lag_cum_Sigma3 * Sigma_3 + Lag_cum_BMm * `B/Mm` + Lag_cum_CEI * CEI + Lag_cum_Log_MV * Log_MV + Lag_cum_Alpha3 * Alpha_3 + Lag_cum_RSI * RSI) %>% 
    ungroup
```

##Returns based on mean36

```{r}
lewellen_expected_return_mean36 <- data.table(lewellen_expected_return_mean36)

setorder(lewellen_expected_return_mean36,ym,Expected_Return_36)

lewellen_expected_return_mean36 <- lewellen_expected_return_mean36[, Decile := ntile(Expected_Return_36, 10), by = ym]

lewellen_expected_return_mean36 <- lewellen_expected_return_mean36[!is.na(MV.USD) & !is.na(RET.USD) & Decile %in% c(1,10)]
```

### Equal Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_mean36_equal <- lewellen_expected_return_mean36 %>% 
  group_by(ym,Decile)%>%
  summarize(ret.port = mean(RET.USD)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_mean36` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_mean36_equal <- as.data.table(portfolio_returns_mean36_equal)
portfolio_returns_mean36_equal[,t.test(`Ret_mean36`)]
```

### Value Weighted Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_mean36_val <- lewellen_expected_return_mean36 %>% 
  group_by(ym,Decile)%>%
  summarize(ret.port = weighted.mean(RET.USD, coalesce(MV.USD, 0), na.rm = T)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_mean36` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_mean36_val <- as.data.table(portfolio_returns_mean36_val)
portfolio_returns_mean36_val[,t.test(`Ret_mean36`)]
```

## Returns based on Cummean

```{r}
lewellen_expected_return_cummean <- data.table(lewellen_expected_return_cummean)

setorder(lewellen_expected_return_cummean,ym,Expected_Return_cummean)

lewellen_expected_return_cummean <- lewellen_expected_return_cummean[, Decile := ntile(Expected_Return_cummean, 10), by = ym]

lewellen_expected_return_cummean <- lewellen_expected_return_cummean[!is.na(MV.USD) & !is.na(RET.USD) & Decile %in% c(1,10)]
```

### Equal Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_cummean_equal <- lewellen_expected_return_cummean %>%
  group_by(ym,Decile)%>%
  summarize(ret.port = mean(RET.USD)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_cummean` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_cummean_equal <- as.data.table(portfolio_returns_cummean_equal)
portfolio_returns_cummean_equal[,t.test(`Ret_cummean`)]
```

### Value Weighted Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_cummean_val <- lewellen_expected_return_cummean %>% 
  group_by(ym,Decile)%>%
  summarize(ret.port = weighted.mean(RET.USD, coalesce(MV.USD, 0), na.rm = T)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_mean36` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_cummean_val <- as.data.table(portfolio_returns_cummean_val)
portfolio_returns_cummean_val[,t.test(`Ret_mean36`)]
```

## regression based on expected return

```{r}
clean_mean <- lewellen_expected_return_mean36 %>% 
  select(Id,ym,RET.USD,ExRET.USD,Expected_Return_36)

clean_mean <- data.table(clean_mean)



reg_mean <- clean_mean[!is.na(Expected_Return_36) &!is.infinite(Expected_Return_36),
                       .(gamma_zero=lm(ExRET.USD~Expected_Return_36)$coefficient[1],
gamma_beta=lm(ExRET.USD~Expected_Return_36)$coefficient[2]),   
  by=ym]


reg_mean[,t.test(gamma_zero)]
reg_mean[,t.test(gamma_beta)]

```
```{r}
clean_cum <- lewellen_expected_return_cummean %>% 
  select(Id,ym,RET.USD,ExRET.USD,Expected_Return_cummean)

clean_cum <- data.table(clean_cum)



reg_cum <- clean_cum[!is.na(Expected_Return_cummean) &!is.infinite(Expected_Return_cummean),
                       .(gamma_zero=lm(ExRET.USD~Expected_Return_cummean)$coefficient[1],
gamma_beta=lm(ExRET.USD~Expected_Return_cummean)$coefficient[2]),   
  by=ym]


reg_cum[,t.test(gamma_zero)]
reg_cum[,t.test(gamma_beta)]

```

## Selected Factors: Log_MV, Alpha_3, RSI

```{r}
# merge with firm characteristics
data_set_3 <- Univariate_Sort_Set_big_small %>% 
  select(Id, ym, MV.USD, RET.USD, MRP.USD, ExRET.USD, Log_MV, Alpha_3, RSI)

lewellen_data_set_3 <- merge(x=data_set_3, y=data_lewellen_3, by.x = c("ym"), by.y = c("ym"), all= 1)


# Creating the lag variable of mean36 average slope
lewellen_data_set_3[, Lag_mean36_Intercept := shift(mean36.intercept, n= 1), by = Id]
lewellen_data_set_3[, Lag_mean36_Log_MV := shift(mean36.gamma.logmv, n= 1), by = Id]
lewellen_data_set_3[, Lag_mean36_Alpha3 := shift(mean36.gamma.alpha3, n= 1), by = Id]
lewellen_data_set_3[, Lag_mean36_RSI := shift(mean36.gamma.rsi, n= 1), by = Id]

# Creating the lag variable of cumulated average slope
lewellen_data_set_3[, Lag_cum_Intercept := shift(cummean.intercept, n= 1), by = Id]
lewellen_data_set_3[, Lag_cum_Log_MV := shift(cummean.gamma.logmv, n= 1), by = Id]
lewellen_data_set_3[, Lag_cum_Alpha3 := shift(cummean.gamma.alpha3, n= 1), by = Id]
lewellen_data_set_3[, Lag_cum_RSI := shift(cummean.gamma.rsi, n= 1), by = Id]

lewellen_expected_return_mean36_3 <- lewellen_data_set_3 %>% 
  group_by(ym, Id) %>% 
  mutate(Expected_Return_36 = Lag_mean36_Intercept * intercept +  Lag_mean36_Log_MV * Log_MV + Lag_mean36_Alpha3 * Alpha_3 + Lag_mean36_RSI * RSI) %>% 
    ungroup

lewellen_expected_return_cummean_3 <- lewellen_data_set_3 %>% 
  group_by(ym, Id) %>% 
  mutate(Expected_Return_cummean = Lag_cum_Intercept * intercept + Lag_cum_Log_MV * Log_MV + Lag_cum_Alpha3 * Alpha_3 + Lag_cum_RSI * RSI) %>% 
    ungroup
```

##Returns based on mean36

```{r}
lewellen_expected_return_mean36_3 <- data.table(lewellen_expected_return_mean36_3)

setorder(lewellen_expected_return_mean36_3,ym,Expected_Return_36)

lewellen_expected_return_mean36_3 <- lewellen_expected_return_mean36_3[, Decile := ntile(Expected_Return_36, 10), by = ym]

lewellen_expected_return_mean36_3 <- lewellen_expected_return_mean36_3[!is.na(MV.USD) & !is.na(RET.USD) & Decile %in% c(1,10)]
```

### Equal Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_mean36_equal_3 <- lewellen_expected_return_mean36_3 %>% 
  group_by(ym,Decile)%>%
  summarize(ret.port = mean(RET.USD)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_mean36` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_mean36_equal_3 <- as.data.table(portfolio_returns_mean36_equal_3)
portfolio_returns_mean36_equal_3[,t.test(`Ret_mean36`)]
```

### Value Weighted Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_mean36_val_3 <- lewellen_expected_return_mean36_3 %>% 
  group_by(ym,Decile)%>%
  summarize(ret.port = weighted.mean(RET.USD, coalesce(MV.USD, 0), na.rm = T)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_mean36` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_mean36_val_3 <- as.data.table(portfolio_returns_mean36_val_3)
portfolio_returns_mean36_val_3[,t.test(`Ret_mean36`)]
```

## Returns based on Cummean

```{r}
lewellen_expected_return_cummean_3 <- data.table(lewellen_expected_return_cummean_3)

setorder(lewellen_expected_return_cummean_3,ym,Expected_Return_cummean)

lewellen_expected_return_cummean_3 <- lewellen_expected_return_cummean_3[, Decile := ntile(Expected_Return_cummean, 10), by = ym]

lewellen_expected_return_cummean_3 <- lewellen_expected_return_cummean_3[!is.na(MV.USD) & !is.na(RET.USD) & Decile %in% c(1,10)]
```

### Equal Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_cummean_equal_3 <- lewellen_expected_return_cummean_3 %>%
  group_by(ym,Decile)%>%
  summarize(ret.port = mean(RET.USD)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_cummean` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_cummean_equal_3 <- as.data.table(portfolio_returns_cummean_equal_3)
portfolio_returns_cummean_equal_3[,t.test(`Ret_cummean`)]
```

### Value Weighted Mean

```{r}
# Long the 10th decile, short the 1st decile and get the return
portfolio_returns_cummean_val_3 <- lewellen_expected_return_cummean_3 %>% 
  group_by(ym,Decile)%>%
  summarize(ret.port = weighted.mean(RET.USD, coalesce(MV.USD, 0), na.rm = T)) %>% 
  spread(Decile,ret.port) %>%
  mutate(`Ret_mean36` = `10`-`1`)

# Test if the return is significantly different from 0
portfolio_returns_cummean_val_3 <- as.data.table(portfolio_returns_cummean_val_3)
portfolio_returns_cummean_val_3[,t.test(`Ret_mean36`)]
```

## regression based on expected return

```{r}
clean_mean_3 <- lewellen_expected_return_mean36_3 %>% 
  select(Id,ym,RET.USD,ExRET.USD,Expected_Return_36)

clean_mean_3 <- data.table(clean_mean_3)



reg_mean_3 <- clean_mean_3[!is.na(Expected_Return_36) &!is.infinite(Expected_Return_36),
                       .(gamma_zero=lm(ExRET.USD~Expected_Return_36)$coefficient[1],
gamma_beta=lm(ExRET.USD~Expected_Return_36)$coefficient[2]),   
  by=ym]


reg_mean_3[,t.test(gamma_zero)]
reg_mean_3[,t.test(gamma_beta)]

```

```{r}
clean_cum_3 <- lewellen_expected_return_cummean_3 %>% 
  select(Id,ym,RET.USD,ExRET.USD,Expected_Return_cummean)

clean_cum_3 <- data.table(clean_cum_3)



reg_cum_3 <- clean_cum_3[!is.na(Expected_Return_cummean) &!is.infinite(Expected_Return_cummean),
                       .(gamma_zero=lm(ExRET.USD~Expected_Return_cummean)$coefficient[1],
gamma_beta=lm(ExRET.USD~Expected_Return_cummean)$coefficient[2]),   
  by=ym]


reg_cum_3[,t.test(gamma_zero)]
reg_cum_3[,t.test(gamma_beta)]

```