---
title: "Portfolio_RET_Calculation"
author: "Yasu"
date: "2023-07-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(zoo)
library(quadprog)
library(IntroCompFinR)
library(tidyr)
library(dplyr)
library(lubridate)
library(data.table)
library(ggplot2)
library(tibble)
```

## Change the data format
### weighted_result_quarterly_6_mean_20
```{r}
weighted_result_quarterly_6_mean_20_complete <- weighted_result_quarterly_6_mean_20 %>%
  mutate(ym=rownames(weighted_result_quarterly_6_mean_20)) %>%
  mutate(ym=as.Date(ym, "%Y-%m-%d")) %>%
  select(ym, everything()) %>%
  mutate_all(~replace(., is.na(.), -Inf)) %>%
  complete(ym = seq.Date(min(ym), as.Date("2021-12-01"), by="month")) %>%
  fill(names(.), .direction= "down") %>%
  mutate_all(~replace(., is.infinite(.), NA)) %>%
  mutate(ym=format(ym, format="%Y-%m-%d"))
```

### weighted_result_quarterly_3_mean_20
```{r}
weighted_result_quarterly_3_mean_20_complete <- weighted_result_quarterly_3_mean_20 %>%
  mutate(ym=rownames(weighted_result_quarterly_3_mean_20)) %>%
  mutate(ym=as.Date(ym, "%Y-%m-%d")) %>%
  select(ym, everything()) %>%
  mutate_all(~replace(., is.na(.), -Inf)) %>%
  complete(ym = seq.Date(min(ym), as.Date("2021-12-01"), by="month")) %>%
  fill(names(.), .direction= "down") %>%
  mutate_all(~replace(., is.infinite(.), NA)) %>%
  mutate(ym=format(ym, format="%Y-%m-%d"))
```

### weighted_result_quarterly_6_cum_20
```{r}
weighted_result_quarterly_6_cum_20_complete <- weighted_result_quarterly_6_cum_20 %>%
  mutate(ym=rownames(weighted_result_quarterly_6_cum_20)) %>%
  mutate(ym=as.Date(ym, "%Y-%m-%d")) %>%
  select(ym, everything()) %>%
  mutate_all(~replace(., is.na(.), -Inf)) %>%
  complete(ym = seq.Date(min(ym), as.Date("2021-12-01"), by="month")) %>%
  fill(names(.), .direction= "down") %>%
  mutate_all(~replace(., is.infinite(.), NA)) %>%
  mutate(ym=format(ym, format="%Y-%m-%d"))
```


### weighted_result_quarterly_3_cum_20
```{r}
weighted_result_quarterly_3_cum_20_complete <- weighted_result_quarterly_3_cum_20 %>%
  mutate(ym=rownames(weighted_result_quarterly_3_cum_20)) %>%
  mutate(ym=as.Date(ym, "%Y-%m-%d")) %>%
  select(ym, everything()) %>%
  mutate_all(~replace(., is.na(.), -Inf)) %>%
  complete(ym = seq.Date(min(ym), as.Date("2021-12-01"), by="month")) %>%
  fill(names(.), .direction= "down") %>%
  mutate_all(~replace(., is.infinite(.), NA)) %>%
  mutate(ym=format(ym, format="%Y-%m-%d"))
```

### weighted_result_quarterly_5_var_20
```{r}
weighted_result_quarterly_5_var_20_complete <- weighted_result_quarterly_5_var_20 %>%
  mutate(ym=rownames(weighted_result_quarterly_5_var_20)) %>%
  mutate(ym=as.Date(ym, "%Y-%m-%d")) %>%
  select(ym, everything()) %>%
  mutate_all(~replace(., is.na(.), -Inf)) %>%
  complete(ym = seq.Date(min(ym), as.Date("2021-12-01"), by="month")) %>%
  fill(names(.), .direction= "down") %>%
  mutate_all(~replace(., is.infinite(.), NA)) %>%
  mutate(ym=format(ym, format="%Y-%m-%d"))
```



### weighted_result_quarterly_3_var_20
```{r}
weighted_result_quarterly_3_var_20_complete <- weighted_result_quarterly_3_var_20 %>%
  mutate(ym=rownames(weighted_result_quarterly_3_var_20)) %>%
  mutate(ym=as.Date(ym, "%Y-%m-%d")) %>%
  select(ym, everything()) %>%
  mutate_all(~replace(., is.na(.), -Inf)) %>%
  complete(ym = seq.Date(min(ym), as.Date("2021-12-01"), by="month")) %>%
  fill(names(.), .direction= "down") %>%
  mutate_all(~replace(., is.infinite(.), NA)) %>%
  mutate(ym=format(ym, format="%Y-%m-%d"))
```


## Performance
```{r}
load("../Original_Dataset/GBR_DS_monthly.RData")
DS.monthly$ym <- as.Date(DS.monthly$ym)
```

###quarterly_6_mean_20
```{r}

t5 <- weighted_result_quarterly_6_mean_20_complete %>% 
  pivot_longer(cols = -ym, names_to = "Id", values_to = "weight")

class(t5$ym)

class(DS.monthly$ym)
t5$ym <- as.Date(t5$ym)

t6 <- DS.monthly %>%
  full_join(t5, by = c("Id", "ym")) %>% 
  select(Id, ym, weight, RET.USD)

t7 <- t6 %>% 
  filter(!is.na(weight) & !is.na(RET.USD)) %>% 
  arrange(ym)

quarterly_6_mean_performance <- t7 %>% 
  group_by(ym) %>% 
  summarise(RET = sum(weight * RET.USD)) %>% 
  ungroup %>% 
  filter(ym >= "1990-01-01")

print(mean(quarterly_6_mean_performance$RET))
print(sd(quarterly_6_mean_performance$RET))
print(mean(quarterly_6_mean_performance$RET)/sd(quarterly_6_mean_performance$RET))

a <- mean(quarterly_6_mean_performance$RET) *0.01
print((1+a)^12-1)


# Plot
ggplot(quarterly_6_mean_performance, aes(x = ym, y = RET)) +
  geom_line() +
  labs(x = "ym", y = "Return") +
  ggtitle("quarterly_6_mean_20")


# Turnover
Turnover_6_mean <- t5 %>% 
  mutate(weight = replace_na(weight, 0)) %>%
  arrange(Id, ym) %>% 
  group_by(Id) %>%
  mutate(weight_1 = lead(weight)) %>% 
  ungroup

Turnover_r_6_mean <- Turnover %>% 
  mutate(abs = abs(weight_1 - weight))%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(abs))%>% 
  mutate(sigma = replace_na(sigma, 0))

print(sum(Turnover_r$sigma))
print(n_distinct(Turnover_r$ym))
print(sum(Turnover_r$sigma)/n_distinct(Turnover_r$ym)/2)


# Effective N 
Effective_N_6_mean <- t7 %>% 
  mutate(w2 = weight^2)%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(w2)) %>% 
  mutate(sigma_i = sigma^(-1))

print(sum(Effective_N_6_mean$sigma_i)/n_distinct(Effective_N_6_mean$ym))


```

```{r}
quarterly_6_mean_performance$ym <- as.Date(as.yearmon(quarterly_6_mean_performance$ym,"%Y.%m"))

tseri_quarterly_6_mean_performance <- quarterly_6_mean_performance[,2]
rownames(tseri_quarterly_6_mean_performance) <- quarterly_6_mean_performance$ym
cumu_quarterly_6_mean_performance <- cumsum(tseri_quarterly_6_mean_performance)

rownames(cumu_quarterly_6_mean_performance) <- quarterly_6_mean_performance$ym
write.csv(cumu_quarterly_6_mean_performance,file = "6_mean_cumulative_return.csv")
```


###quarterly_6_cum_20
```{r}
t5 <- weighted_result_quarterly_6_cum_20_complete %>% 
  pivot_longer(cols = -ym, names_to = "Id", values_to = "weight")

class(t5$ym)

class(DS.monthly$ym)
t5$ym <- as.Date(t5$ym)

t6 <- DS.monthly %>%
  full_join(t5, by = c("Id", "ym")) %>% 
  select(Id, ym, weight, RET.USD)

t7 <- t6 %>% 
  filter(!is.na(weight) & !is.na(RET.USD)) %>% 
  arrange(ym)

quarterly_6_cum_performance <- t7 %>% 
  group_by(ym) %>% 
  summarise(RET = sum(weight * RET.USD)) %>% 
  ungroup%>% 
  filter(ym >= "1990-01-01")

print(mean(quarterly_6_cum_performance$RET))
print(sd(quarterly_6_cum_performance$RET))
print(mean(quarterly_6_cum_performance$RET)/sd(quarterly_6_cum_performance$RET))

a <- mean(quarterly_6_cum_performance$RET) *0.01
print((1+a)^12-1)



# Plot
ggplot(quarterly_6_cum_performance, aes(x = ym, y = RET)) +
  geom_line() +
  labs(x = "ym", y = "Return") +
  ggtitle("quarterly_6_cum_20")


# Turnover
Turnover_6_cum <- t5 %>% 
  mutate(weight = replace_na(weight, 0)) %>%
  arrange(Id, ym) %>% 
  group_by(Id) %>%
  mutate(weight_1 = lead(weight)) %>% 
  ungroup

Turnover_6_cum <- Turnover_6_cum %>% 
  mutate(abs = abs(weight_1 - weight))%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(abs))%>% 
  mutate(sigma = replace_na(sigma, 0))

print(sum(Turnover_6_cum$sigma))
print(n_distinct(Turnover_6_cum$ym))
print(sum(Turnover_6_cum$sigma)/n_distinct(Turnover_6_cum$ym)/2)


# Effectiv N 
Effectiv_N_6_cum <- t7 %>% 
  mutate(w2 = weight^2)%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(w2)) %>% 
  mutate(sigma_i = sigma^(-1))

print(sum(Effectiv_N_6_cum$sigma_i)/n_distinct(Effectiv_N_6_cum$ym))
```

```{r}
quarterly_6_cum_performance$ym <- as.Date(as.yearmon(quarterly_6_cum_performance$ym,"%Y.%m"))

tseri_quarterly_6_cum_performance <- quarterly_6_cum_performance[,2]
rownames(tseri_quarterly_6_cum_performance) <- quarterly_6_cum_performance$ym
cumu_quarterly_6_cum_performance <- cumsum(tseri_quarterly_6_cum_performance)

rownames(cumu_quarterly_6_cum_performance) <- quarterly_6_cum_performance$ym
write.csv(cumu_quarterly_6_cum_performance,file = "6_cum_cumulative_return.csv")
```


###quarterly_3_mean_20
```{r}
t5 <- weighted_result_quarterly_3_mean_20_complete %>% 
  pivot_longer(cols = -ym, names_to = "Id", values_to = "weight")

class(t5$ym)

class(DS.monthly$ym)
t5$ym <- as.Date(t5$ym)

t6 <- DS.monthly %>%
  full_join(t5, by = c("Id", "ym")) %>% 
  select(Id, ym, weight, RET.USD)

t7 <- t6 %>% 
  filter(!is.na(weight) & !is.na(RET.USD)) %>% 
  arrange(ym)

quarterly_3_mean_performance <- t7 %>% 
  group_by(ym) %>% 
  summarise(RET = sum(weight * RET.USD)) %>% 
  ungroup%>% 
  filter(ym >= "1990-01-01")

print(mean(quarterly_3_mean_performance$RET))
print(sd(quarterly_3_mean_performance$RET))
print(mean(quarterly_3_mean_performance$RET)/sd(quarterly_3_mean_performance$RET))

a <- mean(quarterly_3_mean_performance$RET) *0.01
print((1+a)^12-1)



#Plot
ggplot(quarterly_3_mean_performance, aes(x = ym, y = RET)) +
  geom_line() +
  labs(x = "ym", y = "Return") +
  ggtitle("quarterly_3_mean_20")


# Turnover
Turnover_3_mean <- t5 %>% 
  mutate(weight = replace_na(weight, 0)) %>%
  arrange(Id, ym) %>% 
  group_by(Id) %>%
  mutate(weight_1 = lead(weight)) %>% 
  ungroup

Turnover_3_mean <- Turnover_3_mean %>% 
  mutate(abs = abs(weight_1 - weight))%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(abs))%>% 
  mutate(sigma = replace_na(sigma, 0))

print(sum(Turnover_3_mean$sigma))
print(n_distinct(Turnover_3_mean$ym))
print(sum(Turnover_3_mean$sigma)/n_distinct(Turnover_3_mean$ym)/2)


# Effectiv N 
Effectiv_N_3_mean <- t7 %>% 
  mutate(w2 = weight^2)%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(w2)) %>% 
  mutate(sigma_i = sigma^(-1))

print(sum(Effectiv_N_3_mean$sigma_i)/n_distinct(Effectiv_N_3_mean$ym))
```
```{r}
quarterly_3_mean_performance$ym <- as.Date(as.yearmon(quarterly_3_mean_performance$ym,"%Y.%m"))

tseri_quarterly_3_mean_performance <- quarterly_3_mean_performance[,2]
rownames(tseri_quarterly_3_mean_performance) <- quarterly_3_mean_performance$ym
cumu_quarterly_3_mean_performance <- cumsum(tseri_quarterly_3_mean_performance)

rownames(cumu_quarterly_3_mean_performance) <- quarterly_3_mean_performance$ym
write.csv(cumu_quarterly_3_mean_performance,file = "3_mean_cumulative_return.csv")
```



###quarterly_3_cum_20
```{r}
t5 <- weighted_result_quarterly_3_cum_20_complete %>% 
  pivot_longer(cols = -ym, names_to = "Id", values_to = "weight")

class(t5$ym)

class(DS.monthly$ym)
t5$ym <- as.Date(t5$ym)

t6 <- DS.monthly %>%
  full_join(t5, by = c("Id", "ym")) %>% 
  select(Id, ym, weight, RET.USD)

t7 <- t6 %>% 
  filter(!is.na(weight) & !is.na(RET.USD)) %>% 
  arrange(ym)

quarterly_3_cum_performance <- t7 %>% 
  group_by(ym) %>% 
  summarise(RET = sum(weight * RET.USD)) %>% 
  ungroup%>% 
  filter(ym >= "1990-01-01")

print(mean(quarterly_3_cum_performance$RET))
print(sd(quarterly_3_cum_performance$RET))
print(mean(quarterly_3_cum_performance$RET)/sd(quarterly_3_cum_performance$RET))

a <- mean(quarterly_3_cum_performance$RET) *0.01
print((1+a)^12-1)



ggplot(quarterly_3_cum_performance, aes(x = ym, y = RET)) +
  geom_line() +
  labs(x = "ym", y = "Return") +
  ggtitle("quarterly_3_cum_20")


# Turnover
Turnover_3_cum <- t5 %>% 
  mutate(weight = replace_na(weight, 0)) %>%
  arrange(Id, ym) %>% 
  group_by(Id) %>%
  mutate(weight_1 = lead(weight)) %>% 
  ungroup

Turnover_3_cum <- Turnover_3_cum %>% 
  mutate(abs = abs(weight_1 - weight))%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(abs))%>% 
  mutate(sigma = replace_na(sigma, 0))

print(sum(Turnover_3_cum$sigma))
print(n_distinct(Turnover_3_cum$ym))
print(sum(Turnover_3_cum$sigma)/n_distinct(Turnover_3_cum$ym)/2)


# Effectiv N 
Effectiv_N_3_cum <- t7 %>% 
  mutate(w2 = weight^2)%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(w2)) %>% 
  mutate(sigma_i = sigma^(-1))

print(sum(Effectiv_N_3_cum$sigma_i)/n_distinct(Effectiv_N_3_cum$ym))
```

```{r}
quarterly_3_cum_performance$ym <- as.Date(as.yearmon(quarterly_3_cum_performance$ym,"%Y.%m"))

tseri_quarterly_3_cum_performance <- quarterly_3_cum_performance[,2]
rownames(tseri_quarterly_3_cum_performance) <- quarterly_3_cum_performance$ym
cumu_quarterly_3_cum_performance <- cumsum(tseri_quarterly_3_cum_performance)

rownames(cumu_quarterly_3_cum_performance) <- quarterly_3_cum_performance$ym
write.csv(cumu_quarterly_3_cum_performance,file = "3_cum_cumulative_return.csv")
```


###quarterly_5_var_20
```{r}
t5 <- weighted_result_quarterly_5_var_20_complete %>% 
  pivot_longer(cols = -ym, names_to = "Id", values_to = "weight")

class(t5$ym)

class(DS.monthly$ym)
t5$ym <- as.Date(t5$ym)

t6 <- DS.monthly %>%
  full_join(t5, by = c("Id", "ym")) %>% 
  select(Id, ym, weight, RET.USD)

t7 <- t6 %>% 
  filter(!is.na(weight) & !is.na(RET.USD)) %>% 
  arrange(ym)

quarterly_5_var_performance <- t7 %>% 
  group_by(ym) %>% 
  summarise(RET = sum(weight * RET.USD)) %>% 
  ungroup%>% 
  filter(ym >= "1990-01-01")

print(mean(quarterly_5_var_performance$RET))
print(sd(quarterly_5_var_performance$RET))
print(mean(quarterly_5_var_performance$RET)/sd(quarterly_5_var_performance$RET))

a <- mean(quarterly_5_var_performance$RET) *0.01
print((1+a)^12-1)

ggplot(quarterly_5_var_performance, aes(x = ym, y = RET)) +
  geom_line() +
  labs(x = "ym", y = "Return") +
  ggtitle("quarterly_5_var_20")


# Turnover
Turnover_5_var <- t5 %>% 
  mutate(weight = replace_na(weight, 0)) %>%
  arrange(Id, ym) %>% 
  group_by(Id) %>%
  mutate(weight_1 = lead(weight)) %>% 
  ungroup

Turnover_5_var <- Turnover_5_var %>% 
  mutate(abs = abs(weight_1 - weight))%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(abs))%>% 
  mutate(sigma = replace_na(sigma, 0))

print(sum(Turnover_5_var$sigma))
print(n_distinct(Turnover_5_var$ym))
print(sum(Turnover_5_var$sigma)/n_distinct(Turnover_5_var$ym)/2)


# Effectiv N 
Effectiv_N_5_var <- t7 %>% 
  mutate(w2 = weight^2)%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(w2)) %>% 
  mutate(sigma_i = sigma^(-1))

print(sum(Effectiv_N_5_var$sigma_i)/n_distinct(Effectiv_N_5_var$ym))
```

###quarterly_3_var_20
```{r}
t5 <- weighted_result_quarterly_3_var_20_complete %>% 
  pivot_longer(cols = -ym, names_to = "Id", values_to = "weight")

class(t5$ym)

class(DS.monthly$ym)
t5$ym <- as.Date(t5$ym)

t6 <- DS.monthly %>%
  full_join(t5, by = c("Id", "ym")) %>% 
  select(Id, ym, weight, RET.USD)

t7 <- t6 %>% 
  filter(!is.na(weight) & !is.na(RET.USD)) %>% 
  arrange(ym)

quarterly_3_var_performance <- t7 %>% 
  group_by(ym) %>% 
  summarise(RET = sum(weight * RET.USD)) %>% 
  ungroup%>% 
  filter(ym >= "1990-01-01")

print(mean(quarterly_3_var_performance$RET))
print(sd(quarterly_3_var_performance$RET))
print(mean(quarterly_3_var_performance$RET)/sd(quarterly_3_var_performance$RET))

ggplot(quarterly_3_var_performance, aes(x = ym, y = RET)) +
  geom_line() +
  labs(x = "ym", y = "Return") +
  ggtitle("quarterly_3_var_20")


# Turnover
Turnover_3_var <- t5 %>% 
  mutate(weight = replace_na(weight, 0)) %>%
  arrange(Id, ym) %>% 
  group_by(Id) %>%
  mutate(weight_1 = lead(weight)) %>% 
  ungroup

Turnover_3_var <- Turnover_3_var %>% 
  mutate(abs = abs(weight_1 - weight))%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(abs))%>% 
  mutate(sigma = replace_na(sigma, 0))

print(sum(Turnover_3_var$sigma))
print(n_distinct(Turnover_3_var$ym))
print(sum(Turnover_3_var$sigma)/n_distinct(Turnover_3_var$ym)/2)


# Effectiv N 
Effectiv_N_3_var <- t7 %>% 
  mutate(w2 = weight^2)%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(w2)) %>% 
  mutate(sigma_i = sigma^(-1))

print(sum(Effectiv_N_3_var$sigma_i)/n_distinct(Effectiv_N_3_var$ym))
```



```{r}
save(quarterly_6_mean_performance, file = "/Users/kojimadamsimith/Desktop/Summer Semester/Advanced Seminar/GBR/SS23_Empirical-Asset-Pricing/Performance/visual_annual&cumulative_result/mean_6_performance.RData")
save(quarterly_6_cum_performance, file = "/Users/kojimadamsimith/Desktop/Summer Semester/Advanced Seminar/GBR/SS23_Empirical-Asset-Pricing/Performance/visual_annual&cumulative_result/mean_3_performance.RData")
save(quarterly_3_mean_performance, file = "/Users/kojimadamsimith/Desktop/Summer Semester/Advanced Seminar/GBR/SS23_Empirical-Asset-Pricing/Performance/visual_annual&cumulative_result/cum_6_performance.RData")
save(quarterly_3_cum_performance, file = "/Users/kojimadamsimith/Desktop/Summer Semester/Advanced Seminar/GBR/SS23_Empirical-Asset-Pricing/Performance/visual_annual&cumulative_result/cum_3_performance.RData")
```


## Market Return
```{r}
load("../Univariate_Sort_Set.RData")
Univariate_Sort_Set <- as.data.table(Univariate_Sort_Set)

stock_size <- Univariate_Sort_Set
setorder(stock_size, ym, -MV.USD)
stock_big_small <- stock_size[!is.na(MV.USD), .(big_small = ifelse(((cumsum(MV.USD)/sum(MV.USD))>=0.97), 0, 1), Id), by=ym]
stock_big_small <- stock_big_small[big_small==1, c("Id", "ym")]
Univariate_Sort_Set_big_small <- merge(stock_big_small, Univariate_Sort_Set)
```

```{r}
Market_RET <- Univariate_Sort_Set_big_small %>% 
  select(Id, ym, RET.USD, MV.USD) %>% 
  group_by(ym) %>% 
  mutate(MRET = weighted.mean(RET.USD, coalesce(MV.USD, 0), na.rm = T)) %>% 
  ungroup %>% 
  arrange(ym, Id)

Market_RET_ym <- Market_RET %>% 
  group_by(ym) %>% 
  summarise(Market_RET = mean(MRET))

write.csv(Market_RET_ym, file = "/Users/kojimadamsimith/Desktop/Summer Semester/Advanced Seminar/GBR/SS23_Empirical-Asset-Pricing/Market_RET.csv")

Market_RET_ym <- Market_RET_ym %>% 
  mutate(Market_RET = Market_RET*0.01)

mean_month <- mean(Market_RET_ym$Market_RET)
mean_year <- (1+mean_month)^12-1

print(mean_month)
print(mean_year)

```

### Out Performance
```{r}
annual_6_cum_cumulative_return <- annual_6_cum_cumulative_return %>% 
  select(year, ANNUAL_RET.USD)



out_performance <- annual_6_cum_cumulative_return %>% 
  inner_join(annual_market_ret, by = "year") %>% 
  mutate(outperformance = ANNUAL_RET.USD- ANNUAL_MKT_RET.USD)

mean(out_performance$outperformance)
mean(out_performance$ANNUAL_RET.USD)

mean(out_performance$ANNUAL_RET.USD)/sd(out_performance$ANNUAL_RET.USD)

mean(out_performance$ANNUAL_MKT_RET.USD)
```

```{r}
TE <- sd(out_performance$outperformance)
print(TE)
```

```{r}
IR <- mean(out_performance$outperformance)/TE
print(IR)
```



```{r}
DTB <- DTB6_monthly %>% 
  filter(ym > 1983.11) %>% 
  group_by(ym) %>% 
  summarise(rf = mean(DTB6))

(1+mean(DTB$rf)*0.01)^12-1



SR <- (mean(out_performance$ANNUAL_RET.USD)-mean(DTB$rf))/sd(out_performance$ANNUAL_RET.USD)
print(SR)
```



## Style Analysis
### 6 mean
```{r}

mean_6 <- quarterly_6_mean_performance

mean_6$ym <- format(mean_6$ym, "%Y.%m")


StyleAnalysis_Set_mean_6 <- merge(StyleAnalysis_FF_and_Mom_Set,mean_6,by="ym")

Style_Analysis_Model <- lm(RET~SMB+HML+CMA+RMW+WML, data=StyleAnalysis_Set_mean_6)

summary(Style_Analysis_Model)
```
### 6 cum

```{r}
cum_6 <- quarterly_6_cum_performance

cum_6$ym <- format(cum_6$ym, "%Y.%m")


StyleAnalysis_Set_cum_6 <- merge(StyleAnalysis_FF_and_Mom_Set,cum_6,by="ym")

Style_Analysis_Model <- lm(RET~SMB+HML+CMA+RMW+WML, data=StyleAnalysis_Set_cum_6)

summary(Style_Analysis_Model)

```
### 3 mean
```{r}
mean_3 <- quarterly_3_mean_performance

mean_3$ym <- format(mean_3$ym, "%Y.%m")


StyleAnalysis_Set_mean_3 <- merge(StyleAnalysis_FF_and_Mom_Set,mean_3,by="ym")

Style_Analysis_Model <- lm(RET~SMB+HML+CMA+RMW+WML, data=StyleAnalysis_Set_mean_3)

summary(Style_Analysis_Model)

```

### 3 cum
```{r}
cum_3 <- quarterly_3_cum_performance

cum_3$ym <- format(cum_3$ym, "%Y.%m")


StyleAnalysis_Set_cum_3 <- merge(StyleAnalysis_FF_and_Mom_Set,cum_3,by="ym")

Style_Analysis_Model <- lm(RET~SMB+HML+CMA+RMW+WML, data=StyleAnalysis_Set_cum_3)

summary(Style_Analysis_Model)
```

## 5 var
```{r}
var_5 <- quarterly_5_var_performance

var_5$ym <- format(var_5$ym, "%Y.%m")


StyleAnalysis_Set_var_5 <- merge(StyleAnalysis_FF_and_Mom_Set,var_5,by="ym")

Style_Analysis_Model <- lm(RET~SMB+HML+CMA+RMW+WML, data=StyleAnalysis_Set_var_5)

summary(Style_Analysis_Model)
```



## 3 var
```{r}
var_3 <- quarterly_3_var_performance

var_3$ym <- format(var_3$ym, "%Y.%m")


StyleAnalysis_Set_var_3 <- merge(StyleAnalysis_FF_and_Mom_Set,var_3,by="ym")

Style_Analysis_Model <- lm(RET~SMB+HML+CMA+RMW+WML, data=StyleAnalysis_Set_var_3)

summary(Style_Analysis_Model)
```
```{r}
Ids <- quarterly_6_cum_20 %>% 
  inner_join(DS.static, by = c("Id")) %>% 
  select(Id, ym, NAME)
```

