---
title: "visual_cumu_3_mean_20"
author: "Yu"
date: "2023-07-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(zoo)
library(quadprog)
library(IntroCompFinR)
library(tidyr)
library(dplyr)
library(lubridate)
library(data.table)
library(ggplot2)
library(tibble)
library(PerformanceAnalytics)
```


## Change the data format
### weighted_result_quarterly_3_var_20
```{r}

weighted_result_quarterly_3_mean_20_complete <- weighted_result_quarterly_3_mean_20 %>%
  mutate(ym=rownames(weighted_result_quarterly_3_mean_20)) %>%
  mutate(ym=as.Date(ym, "%Y-%m-%d")) %>%
  select(ym, everything()) %>%
  mutate_all(~replace(., is.na(.), -Inf)) %>%
  complete(ym = seq.Date(min(ym), as.Date("2021-12-01"), by="month")) %>%
  fill(names(.), .direction= "down") %>%
  mutate_all(~replace(., is.infinite(.), NA)) %>%
  mutate(ym=format(ym, format="%Y-%m-%d"))
```

###quarterly_3_mean_20
```{r}
t5 <- weighted_result_quarterly_3_mean_20_complete %>% 
  pivot_longer(cols = -ym, names_to = "Id", values_to = "weight")

class(t5$ym)

class(DS.monthly$ym)
t5$ym <- as.yearmon(t5$ym)

t6 <- DS.monthly %>%
  full_join(t5, by = c("Id", "ym")) %>% 
  select(Id, ym, weight, RET.USD)

t7 <- t6 %>% 
  filter(!is.na(weight) & !is.na(RET.USD)) %>% 
  arrange(ym) 


quarterly_3_mean_performance <- t7 %>% 
  group_by(ym) %>% 
  summarise(RET = sum(weight * RET.USD)) %>% 
  ungroup %>% filter(ym >= "1990-01-01")

print(mean(quarterly_3_mean_performance$RET))
print(sd(quarterly_3_mean_performance$RET))
print(mean(quarterly_3_mean_performance$RET)/sd(quarterly_3_mean_performance$RET))


write.csv(quarterly_3_mean_performance, file = "mean_3_performance.csv")
```


```{r}
anualized_return <- (1+mean(quarterly_3_mean_performance$RET) *0.01)^12-1
print(anualized_return)
```


```{r}
quarterly_3_mean_performance$ym <- as.Date(as.yearmon(quarterly_3_mean_performance$ym,"%Y.%m"))

tseri_quarterly_3_mean_performance <- quarterly_3_mean_performance[,2]
rownames(tseri_quarterly_3_mean_performance) <- quarterly_3_mean_performance$ym
cumu_quarterly_3_mean_performance <- cumsum(tseri_quarterly_3_mean_performance)

rownames(cumu_quarterly_3_mean_performance) <- quarterly_3_var_performance$ym
write.csv(cumu_quarterly_3_mean_performance,file = "3_mean_cumulative_return.csv")
```


```{r}
# Turnover
Turnover_3_mean <- t5 %>% 
  mutate(weight = replace_na(weight, 0)) %>%
  arrange(Id, ym) %>% 
  group_by(Id) %>%
  mutate(weight_1 = lead(weight)) %>% 
  ungroup

Turnover_3_mean <- Turnover_3_mean %>% 
  mutate(abs = abs(weight_1 - weight))%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(abs))%>% 
  mutate(sigma = replace_na(sigma, 0))

print(sum(Turnover_3_mean$sigma))
print(n_distinct(Turnover_3_mean$ym))
print(sum(Turnover_3_mean$sigma)/n_distinct(Turnover_3_mean$ym)/2)


# Effectiv N 
Effectiv_N_3_mean <- t7 %>% 
  mutate(w2 = weight^2)%>% 
  group_by(ym) %>% 
  summarise(sigma = sum(w2)) %>% 
  mutate(sigma_i = sigma^(-1))

print(sum(Effectiv_N_3_mean$sigma_i)/n_distinct(Effectiv_N_3_mean$ym))